Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-07 bbbq_article.tex
Improve abstract, use SARS-CoV-2 and Mycobacterium tuberculosis instead of 'COVID/covid' and 'Mycobacterium/myco'

The human immune system is unexpectedly attentive towards
human transmembrane helices (TMHs), as TMH-derived peptide fragments
bind to histocompatibility complex (MHC) class I more often then expected
by chance only.
This finding hints that there has been selection upon detecting TMH-derived
peptides in pathogens.
If this signature of selection is present in MHC-II is unknown.
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to peptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, using an innovative computation method, 
we show that natural selection on TMHs is [strong enough/still too weak]
to detect.
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has 
left [a clear/a weak/no]
signal in the evolutionary history of the pathogen.

@@

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-1, MHC-I, MHC-2, MHC-II, COVID-19

@@

Transmembrane helices are conserved structures that span
a cell membrane with an alpha helix.
TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Polypeptide fragments derived from TMHs are among the most hydrophobic,
together with the internals of soluble proteins, where the
hydrophobicity parts guide the protein to achieve its 3D configuration.
TMHs are general structures: 25 percent of the human proteome is
anchored by at least one TMH. COVID-19 has 21 TMHs, 
making up for \richel{?} percent of its entire genome.
There are multiple computational tools developed to predict which
parts of membrane proteins are TMH.

@@

In general, on would hope that evolutionary selection results in
an immune system that as most attentive for loci that are
essential for a virus, as these will be most conserved.
In COVID-19, for example, there is preliminary evidence that the strongest
selection pressure is upon residues that changes its 
virulence \cite{velazquez2020positive}.
These loci, however, only account for a small part of a pathogen's proteome.
Additionally, these essential parts differ widely between pathogens.
Because of this scarcity and variance in targets, 
one can imagine that the human immune system 
is not tailored to detect these sites, 
as hinted by upon by the aforementioned influenza study.

@@

To determine the percentages of epitopes overlapping
with TMHs, we use three reference proteomes, which are
a human, viral and bacterial one.
For a human reference proteome, we used the Uniprot human reference proteome
from \url{https://www.uniprot.org/proteomes/UP000005640}), 
which is the same as \cite{bianchi2017}.
The viral reference proteome is represented by
the proteome of the first sequenced COVID-19 strain (\cite{wu2020new},
GenBank ID of MN908947.3, \url{https://www.ncbi.nlm.nih.gov/nuccore/MN908947})
For bacteria, we used the Uniprot Mycobacterium tuberculosis reference genome
(\url{https://www.uniprot.org/proteomes/UP000001584}) is used.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, COVID-19 and Mycobacterium proteome.
  }
  \label{fig:2}
\end{figure}

@@

We concluded that the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its viral pathogen.
Because the full COVID-19 has 21 TMHs, the percentages
of MHC-I epitopes being part of a TMH are likelier to be affected by
stochasticity. We chose to use COVID-19 regardless, as the thousands
of its time-dated genomic sequences are ideal for determining the 
evolutionary conservation of MHC-I detecting TMHs.

@@

%\begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and COVID-19 for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_myco}
% \end{table}

@@

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and COVID-19 for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_myco}
% \end{table}

>>>>

The human immune system is unexpectedly attentive towards
human transmembrane helices (TMHs), as TMH-derived peptide fragments
bind to histocompatibility complex (MHC) class I more often then expected
by chance only.
This finding hints that there has been selection upon detecting TMH-derived
peptides in pathogens.
If this signature of selection is present in MHC-II is unknown.
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to peptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, we show the TMHs are [more/less/equally] 
conserved.
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has 
left [a clear/a weak/no]
signal in the evolutionary history of the pathogen.

@@

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, SARS-CoV-2

@@

Transmembrane helices are conserved structures that span
a cell membrane with an alpha helix.
TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Polypeptide fragments derived from TMHs are among the most hydrophobic,
together with the internals of soluble proteins, where the
hydrophobicity parts guide the protein to achieve its 3D configuration.
TMHs are general structures: 25 percent of the human proteome is
anchored by at least one TMH. SARS-CoV-2 has 21 TMHs, 
making up for \richel{?} percent of its entire genome.
There are multiple computational tools developed to predict which
parts of membrane proteins are TMH.

@@

In general, on would hope that evolutionary selection results in
an immune system that as most attentive for loci that are
essential for a virus, as these will be most conserved.
In SARS-CoV-2, for example, there is preliminary evidence that the strongest
selection pressure is upon residues that changes its 
virulence \cite{velazquez2020positive}.
These loci, however, only account for a small part of a pathogen's proteome.
Additionally, these essential parts differ widely between pathogens.
Because of this scarcity and variance in targets, 
one can imagine that the human immune system 
is not tailored to detect these sites, 
as hinted by upon by the aforementioned influenza study.

@@

To determine the percentages of epitopes overlapping
with TMHs, we use three reference proteomes, which are
a human, viral and bacterial one.
For a human reference proteome, we used the Uniprot human reference proteome
from \url{https://www.uniprot.org/proteomes/UP000005640}), 
which is the same as \cite{bianchi2017}.
The viral reference proteome is represented by
the proteome of the first sequenced SARS-CoV-2 strain (\cite{wu2020new},
GenBank ID of MN908947.3, \url{https://www.ncbi.nlm.nih.gov/nuccore/MN908947})
For bacteria, we used the Uniprot Mycobacterium tuberculosis reference genome
(\url{https://www.uniprot.org/proteomes/UP000001584}) is used.

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, SARS-CoV-2 (labeled 'covid') 
    and Mycobacterium tuberculosis (labeled 'myco') proteome. 
  }
  \label{fig:2}
\end{figure}

@@

We concluded that the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its viral pathogen.
Because the full SARS-CoV-2 has 21 TMHs, the percentages
of MHC-I epitopes being part of a TMH are likelier to be affected by
stochasticity. We chose to use SARS-CoV-2 regardless, as the thousands
of its time-dated genomic sequences are ideal for determining the 
evolutionary conservation of MHC-I detecting TMHs.

@@

%\begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium tuberculosis for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_myco}
% \end{table}

@@

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and 
      Mycobacterium tuberculosis for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_myco}
% \end{table}
